R Notebook

### 2018-10-16 main_bookcliff.Rmd
finished cleaning

now we need to find the corresponding thresholds
given that d1 is only found in e2, its threshold is computed with its general proportion
but this is not the case for d2
we need first to compute the thresholds of d2 because will impact threshold of d1
```{r}
qd2e2=qnorm(1-pd2e2)
qd1e2=qnorm(1-pd2e2-pd1e2)
qd2e3=qnorm(1-pd2e3)
c(qd2e2,qd1e2,qd2e3)
```
Now I can do the simulation
The gibbs sampling is different that in the Latemar because the truncation rule is different and adptative

```{r}
par(bg="transparent")
n=dim(gridprop1)
gridprop1<-gridprop2<-err<-array(NA,c(100,20,566))
gridprop1[5,10,]<-prop1mat[,1]
gridprop1[15,9,]<-prop1mat[,2]
gridprop1[25,10,]<-prop1mat[,3]
gridprop1[35,9,]<-prop1mat[,4]
gridprop1[45,10,]<-prop1mat[,5]
gridprop1[55,9,]<-prop1mat[,6]
gridprop1[65,10,]<-prop1mat[,7]
gridprop1[75,9,]<-prop1mat[,8]
gridprop1[99,10,]<-prop1mat[,9]
#gridprop1[is.na(grid)]=NA
gridprop2[5,10,]<-prop2mat[,1]
gridprop2[15,9,]<-prop2mat[,2]
gridprop2[25,10,]<-prop2mat[,3]
gridprop2[35,9,]<-prop2mat[,4]
gridprop2[45,10,]<-prop2mat[,5]
gridprop2[55,9,]<-prop2mat[,6]
gridprop2[65,10,]<-prop2mat[,7]
gridprop2[75,9,]<-prop2mat[,8]
gridprop2[99,10,]<-prop2mat[,9]
#gridprop2[is.na(grid)]=NA
gridprop3=1-gridprop1-gridprop2
gridprop1=gridprop1-p1
gridprop2=gridprop2-p2
gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
gridprop2krig<-prop_kriging(gridprop2,500,20,20,0.1)
# we are trying here to have the same proportions on every y plane (because no information on them but still want non sationarity)
for (y in 1:20){
  if (y!=10 & y!=9){
    gridprop1krig[,y,]=gridprop1krig[,10,]
    gridprop2krig[,y,]=gridprop2krig[,10,]
  }
}

#now we need to retrend the results
gridprop1krig=gridprop1krig+p1
gridprop2krig=gridprop2krig+p2
gridprop3krig=1-gridprop1krig-gridprop2krig # there is a problem  here to solve
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      err[x,y,z]=gridprop1krig[x,y,z]+gridprop2krig[x,y,z]
      if (err[x,y,z]>1){
        gridprop1krig[x,y,z]=gridprop1krig[x,y,z]+(1-err[x,y,z])
        gridprop3krig[x,y,z]=0
      }
    }
  }
}

# now that we have the proportions, we can compute the corresponding thresholds
# because there are no correlations between the gaussian functions, the thresholds can be computed analytically
n=dim(gridprop1)
q1tottest=q2tottest=array(NA,c(100,20,566))
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      q1tottest[x,y,z]=qnorm(gridprop1krig[x,y,z])
      if (gridprop3krig[x,y,z]>0) {
        q2tottest[x,y,z]=qnorm(1-(gridprop2krig[x,y,z]/(1-gridprop1krig[x,y,z])))
      }
      else{q2tottest[x,y,z]=-Inf}
    }
  }
}

@@

Y1gibbs<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,3)
image(Y1gibbs[,10,])
image(i1grid[,10,])
image(Y1gibbs[,10,])
image(q1map[,10,])

@@

E1=Y1gibbs-Y1
E2=Y2gibbs-Y2
E1k<-prop_kriging(E1,rh,20,20,0.1)
E2k<-prop_kriging(E2,rh,20,20,0.1)
Y1c=Y1+E1k
Y2c=Y2+E2k
facc<-Y1c
facc[]=3
facc[Y1c<q1tottest]=1
facc[Y1c>q1tottest & Y2c>q2tottest]=2
image(facc[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(grid[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(E1k[,10,],col=heat.colors(300))
image(E2k[,10,],col=heat.colors(300))
dgrid<-array(NA,c(100,20,566))
diag_lat[is.na(diag_lat)]=Inf
dgrid[5,10,]=diag_lat[,1]
dgrid[15,9,]<-diag_lat[,2]
dgrid[25,10,]<-diag_lat[,3]
dgrid[35,9,]<-diag_lat[,4]
dgrid[45,10,]<-diag_lat[,5]
dgrid[55,9,]<-diag_lat[,6]
dgrid[65,10,]<-diag_lat[,7]
dgrid[75,9,]<-diag_lat[,8]
dgrid[99,10,]<-diag_lat[,9]
Y3gibbs<-gibbs_sampling_diag(grid,dgrid,c(qd1e2,qd2e2,qd2e3),0.1,20,10,rv2,rh,rh,b2,3)
image(Y3gibbs[,10,])
facdg<-Y3gibbs
facdg[!is.na(facdg)]=3
facdg[ grid==2 & Y3gibbs<qd2e2 & Y3gibbs>qd1e2]=1
facdg[ grid==2 & Y3gibbs>qd2e2 ]=2
facdg[ grid==3 & Y3gibbs>qd2e3 ]=2
image(facdg[,10,],col=c("green","yellow","black"))
image(dgrid[,10,],col=c("green","yellow","black"))
E3=Y3gibbs-Y3
E3k<-prop_kriging(E3,rh3,20,20,0.1)
Y3c=Y3+E3k
facd<-Y3c
facd[]=3
facd[ facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=1
facd[ facc==2 & Y3c>qd2e2 ]=2
facd[ facc==3 & Y3c>qd2e3 ]=2

image(facd[,10,],col=c("green","yellow","black"))
fac_comb=facc
fac_comb[facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=4
fac_comb[facc==2 & Y3c>qd2e2 ]=5
fac_comb[facc==3 & Y3c>qd2e3 ]=5
image(facc[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(fac_comb[,10,],col=c("darkslategray4","burlywood2","brown3","green","yellow"))
image(dgrid[,10,],col=c("green","yellow","black"))
```

>>>>

now we need to find the corresponding thresholds
given that d1 is only found in e2, its threshold is computed according to its proportion in this facies
but this is not the case for d2 which is present in e2 and e3
we need first to compute the thresholds of d2 because will impact threshold of d1
```{r}
qd2e2=qnorm(1-pd2e2)
qd1e2=qnorm(1-pd2e2-pd1e2)
qd2e3=qnorm(1-pd2e3)
c(qd2e2,qd1e2,qd2e3)
```
Now the simulation is performed
The gibbs sampling is different that in the Latemar because the truncation rule is different and adptative

```{r}
par(bg="transparent")
n=dim(gridprop1)
# local proportions of depositional facies
gridprop1<-gridprop2<-err<-array(NA,c(100,20,566))
gridprop1[5,10,]<-prop1mat[,1]
gridprop1[15,9,]<-prop1mat[,2]
gridprop1[25,10,]<-prop1mat[,3]
gridprop1[35,9,]<-prop1mat[,4]
gridprop1[45,10,]<-prop1mat[,5]
gridprop1[55,9,]<-prop1mat[,6]
gridprop1[65,10,]<-prop1mat[,7]
gridprop1[75,9,]<-prop1mat[,8]
gridprop1[99,10,]<-prop1mat[,9]

gridprop2[5,10,]<-prop2mat[,1]
gridprop2[15,9,]<-prop2mat[,2]
gridprop2[25,10,]<-prop2mat[,3]
gridprop2[35,9,]<-prop2mat[,4]
gridprop2[45,10,]<-prop2mat[,5]
gridprop2[55,9,]<-prop2mat[,6]
gridprop2[65,10,]<-prop2mat[,7]
gridprop2[75,9,]<-prop2mat[,8]
gridprop2[99,10,]<-prop2mat[,9]

# detrend the local proportions by the global proportion before the kriging
gridprop3=1-gridprop1-gridprop2
gridprop1=gridprop1-p1
gridprop2=gridprop2-p2
#kriging
gridprop1krig<-prop_kriging(gridprop1,500,20,20,0.1)
gridprop2krig<-prop_kriging(gridprop2,500,20,20,0.1)

# we put the same proportions on every y plane (because no information in this direction)
for (y in 1:20){
  if (y!=10 & y!=9){
    gridprop1krig[,y,]=gridprop1krig[,10,]
    gridprop2krig[,y,]=gridprop2krig[,10,]
  }
}

#now we need to retrend the results
gridprop1krig=gridprop1krig+p1
gridprop2krig=gridprop2krig+p2
gridprop3krig=1-gridprop1krig-gridprop2krig 
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      err[x,y,z]=gridprop1krig[x,y,z]+gridprop2krig[x,y,z]
      if (err[x,y,z]>1){
        gridprop1krig[x,y,z]=gridprop1krig[x,y,z]+(1-err[x,y,z])
        gridprop3krig[x,y,z]=0
      }
    }
  }
}

# now that we have the proportions, we can compute the corresponding thresholds defined by the truncation rule
# because there are no correlations between the gaussian functions, the thresholds can be computed analytically
n=dim(gridprop1)
q1tottest=q2tottest=array(NA,c(100,20,566))
for (x in 1:n[1]){
  for(y in 1:n[2]){
    for( z in 1:n[3]){
      q1tottest[x,y,z]=qnorm(gridprop1krig[x,y,z])
      if (gridprop3krig[x,y,z]>0) {
        q2tottest[x,y,z]=qnorm(1-(gridprop2krig[x,y,z]/(1-gridprop1krig[x,y,z])))
      }
      else{q2tottest[x,y,z]=-Inf}
    }
  }
}

@@

# the Gibbs sampling for the different Gaussian functions can be done separately
# because there are no correlations between them
Y1gibbs<-gibbs_sampling_map(i1grid,q1map,0.1,20,10,rv1,rh,rh,b1,3)
image(Y1gibbs[,10,])
image(i1grid[,10,])
image(Y1gibbs[,10,])
image(q1map[,10,])

@@

E1=Y1gibbs-Y1
E2=Y2gibbs-Y2
# kriging the error between unconditional and conditional simulation at data points
E1k<-prop_kriging(E1,rh,20,20,0.1)
E2k<-prop_kriging(E2,rh,20,20,0.1)
Y1c=Y1+E1k
Y2c=Y2+E2k
facc<-Y1c
# truncation of the conditioned Gaussian functions
facc[]=3
facc[Y1c<q1tottest]=1
facc[Y1c>q1tottest & Y2c>q2tottest]=2
image(facc[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(grid[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(E1k[,10,],col=heat.colors(300))
image(E2k[,10,],col=heat.colors(300))

#now diagenesis, separately because Gaussian functions not correlated
dgrid<-array(NA,c(100,20,566))
diag_lat[is.na(diag_lat)]=Inf
dgrid[5,10,]=diag_lat[,1]
dgrid[15,9,]<-diag_lat[,2]
dgrid[25,10,]<-diag_lat[,3]
dgrid[35,9,]<-diag_lat[,4]
dgrid[45,10,]<-diag_lat[,5]
dgrid[55,9,]<-diag_lat[,6]
dgrid[65,10,]<-diag_lat[,7]
dgrid[75,9,]<-diag_lat[,8]
dgrid[99,10,]<-diag_lat[,9]
Y3gibbs<-gibbs_sampling_diag(grid,dgrid,c(qd1e2,qd2e2,qd2e3),0.1,20,10,rv2,rh,rh,b2,3)
image(Y3gibbs[,10,])
facdg<-Y3gibbs
facdg[!is.na(facdg)]=3
facdg[ grid==2 & Y3gibbs<qd2e2 & Y3gibbs>qd1e2]=1
facdg[ grid==2 & Y3gibbs>qd2e2 ]=2
facdg[ grid==3 & Y3gibbs>qd2e3 ]=2
image(facdg[,10,],col=c("green","yellow","black"))
image(dgrid[,10,],col=c("green","yellow","black"))
E3=Y3gibbs-Y3
E3k<-prop_kriging(E3,rh3,20,20,0.1)
Y3c=Y3+E3k
facd<-Y3c
facd[]=3
facd[ facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=1
facd[ facc==2 & Y3c>qd2e2 ]=2
facd[ facc==3 & Y3c>qd2e3 ]=2

#final truncation
image(facd[,10,],col=c("green","yellow","black"))
fac_comb=facc
fac_comb[facc==2 & Y3c<qd2e2 & Y3c>qd1e2]=4
fac_comb[facc==2 & Y3c>qd2e2 ]=5
fac_comb[facc==3 & Y3c>qd2e3 ]=5
image(facc[,10,],col=c("darkslategray4","burlywood2","brown3"))
image(fac_comb[,10,],col=c("darkslategray4","burlywood2","brown3","green","yellow"))
image(dgrid[,10,],col=c("green","yellow","black"))
```
